Tabular Constraint Learning

### 2016-04-13 Paper/ECAI/tabular.tex
put my comments

\section{Formalization}
\tias{More gentle}
\samuel{Explain concepts on example}
\subsection{Groups, Type-consistency and Constraints}
In this work we distinguish the following types of data: numeric and textual. The numeric type has two subtypes: integers and floats. We also consider the special element called \textit{None}, which has two types: numeric and textual. A set is called \textit{type-consistent} iff all elements are either numeric or textual. Certain constraints, such as \textit{rank} or \textit{series}, make use of the numeric sub-types by requiring its arguments to be integers.

@@

\section{Problem Statement}
In the previous section we introduced the problem of tabular constraint learning informally using the example in Figure \ref{fig:main_example}. Here we formalize the statement in terms of spreadsheet constraints and group assignments as follows:

@@

\section{Approach to Tabular Constraint Learning}
As we have seen the statement before we assume the set of groups to be given. It is often, however, not the case and a possible approach is to extract the groups from the CSV file directly. In our system, we have implement the group construction step using the type-consistency check. \sergey{Samuel, we need details here, I think} In general, separating data from a header is a task on its own  \cite{header} and goes beyond the scope of this paper.

@@

\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{XXX}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{V_x} & X is integer or textual & All elements in X are different \\
    %X = Y & & \\
    \ecfkey{V_{fk}}{V_{pk}} & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    \eclookupprod{V_r}{V_1}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \eclookup{V_r}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \eclookupfuzzy{V_r}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \ecperm{V_x} & & \\
    \ecprod{V_r}{V_1}{V_2} & & \\
    \ecproj{V_r}{G_x} & & \\
    \ecrank{V_r}{V_1} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{V_r}{V_{pos}}{V_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{V_1} & & \\
    \ecsumc{V_r}{G_1} & & Y is the result of summing each column in X \\
    \ecsumr{V_r}{G_1} & & Y is the result of summing each row in X \\
    \ecsumif{V_r}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \ecsumprod{V_r}{V_1}{V_2} & & \\

>>>>

\section{Formalization}
\tias{More gentle}
\samuel{Explain concepts on example}
\sergey{subgroup notation, rework the solution definition}
\subsection{Groups, Type-consistency and Constraints}
In this work we distinguish the following types of data: numeric and textual. The numeric type has two subtypes: integers and floats. We also consider the special element called \textit{None}, which has two types: numeric and textual. A set is called \textit{type-consistent} iff all elements are either numeric or textual. Certain constraints, such as \textit{rank} or \textit{series}, make use of the numeric sub-types by requiring its arguments to be integers.

@@

\section{Problem Statement}
\sergey{should reflect all the changes, Luc wants to introduce constraint satisfation into problem statement, maybe we should move the definition of a solution here? Like a solution is actually constraint satisfaction?}
In the previous section we introduced the problem of tabular constraint learning informally using the example in Figure \ref{fig:main_example}. Here we formalize the statement in terms of spreadsheet constraints and group assignments as follows:

@@

\section{Approach to Tabular Constraint Learning}
\sergey{Luc wants this to be more intuitive, should we just add some examples here to make it easier to follow and refer to the running example?}
As we have seen the statement before we assume the set of groups to be given. It is often, however, not the case and a possible approach is to extract the groups from the CSV file directly. In our system, we have implement the group construction step using the type-consistency check. \sergey{Samuel, we need details here, I think} In general, separating data from a header is a task on its own  \cite{header} and goes beyond the scope of this paper.

@@

\sergey{Table should take into account our new notation and balance between formality and intuition, heh}
\begin{table*}
  \centering
  \begin{tabularx}{\textwidth}{XXX}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    \ecalldiff{V_x} & X is integer or textual & All elements in X are different \\
    %X = Y & & \\
    \ecfkey{V_{fk}}{V_{pk}} & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    \eclookupprod{V_r}{V_1}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \eclookup{V_r}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \eclookupfuzzy{V_r}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \ecperm{V_x} & & \\
    \ecprod{V_r}{V_1}{V_2} & & \\
    \ecproj{V_r}{G_x} & & \\
    \ecrank{V_r}{V_1} & Y and X have the same length & Y is the rank of X (including ties)\\
    \ectotal{V_r}{V_{pos}}{V_{neg}} & A, P and N have the same length and their length is at least 2 & *\\
    \ecseries{V_1} & & \\
    \ecsumc{V_r}{G_1} & & Y is the result of summing each column in X \\
    \ecsumr{V_r}{G_1} & & Y is the result of summing each row in X \\
    \ecsumif{V_r}{V_{fk}}{V_{pk}}{V_{val}} & & \\
    \ecsumprod{V_r}{V_1}{V_2} & & \\
